Providing A Unified User Environment for Canada National Advanced Computing Centers

### 2019-02-12 extended-abstract.tex
Added section about Gentoo

\section{Introduction}
In 2017, Compute Canada set out to refresh its advanced computing infrastructure by deploying a few large clusters to
replace nearly 30 smaller legacy clusters. This was a good opportunity to rethink our approach to software
installation. Up to this point, each of the legacy clusters required individual manual software installation. This was
laborious because each software package had to be installed tens of times, and it created a poor experience for users
when moving between clusters, due to slight inconsistencies in software installations. When we set out to build a
common software environment to be used on all new clusters, we first established four guiding principles for our design
choices.

@@

\subsection{Gentoo Prefix}
\label{sub:Gentoo_Prefix}

>>>>

\section{Introduction}
\label{sec:Introduction}
In 2017, Compute Canada set out to refresh its advanced computing infrastructure by deploying a few large clusters to
replace nearly 30 smaller legacy clusters. This was a good opportunity to rethink our approach to software
installation. Up to this point, each of the legacy clusters required individual manual software installation. This was
laborious because each software package had to be installed tens of times, and it created a poor experience for users
when moving between clusters, due to slight inconsistencies in software installations. When we set out to build a
common software environment to be used on all new clusters, we first established four guiding principles for our design
choices.

@@

\subsection{Gentoo Prefix}
\label{sub:Gentoo_Prefix}
Gentoo Prefix \cite{Gentoo} is an alternative solution to provide a compatibility layer. It allows to install in a non-default location most packages that make a typical Linux operating system. Contrary to Nix however, it installs packages in a structure that is much more similar to a standard Linux distribution. This is helpful when we need to update packages, and it minimizes problems when an application encounters a dependency that is not installed in a traditional structure. At the time of this writing, we are still experimenting with Gentoo Prefix, and it is not used in production.
